\SW: II. New lens candidates from the CFHTLS discovered through citizen science

### 2014-12-16 doc/sw-cfhtls.tex
rearranged and added many sections and figures but are not yet final
add arc magnitude related figs, final gallery, new title

\title[\sw II]
{\SW: II. Did we beat the lens finding robots in CFHTLS?}

@@

The CFHT Legacy Survey has been searched for strong lenses with
semi-automated algorithms both at galaxy and groups scales. With the aim
of improving these lens finding robots, we carry out a blind lens search
in the complete \cfhtls WIDE survey with \sw. We describe the training
sample used for both training the citizen scientists that participated
in \sw and calibrating their performance. We generate realistic looking
simulated samples of lenses both at galaxy and group-scales as part of
this training sample. We present 74 new strong gravitational lens
candidates discovered from the \sw-\cfhtls search. Furthermore, we
compile a sample of false positives which can be used for robot testing,
first of its kind for the lensing community. The simulated sample is
also used to make a comparison between human performance against the
robots. We find that the XX per cent of the known lens sample is
recovered and the new lens sample has XX completeness with respect to
the simulated sample. We make available the following data products:
simulated sample, simulation code and the false positives sample at XXX.

@@

@@

\subsection{Discovery of new lenses from \sw}
\label{sec:results:disc}

@@

%
%\begin{longtable*}{l c c c c c c c l}
%\caption{ \label{tab:all} 
%Characteristics of lens candidates from the \SA sample. }\\
%ID & RA & Dec &  $i$ & $z_{\rm phot}$ & $R_{\rm A}$ & Rank & Type & previous ID  \\
%    & (hms) & (dms) &  (mag) &   & (arcsec) &  &  & \\ [1.5ex] \hline \\ 
%\endfirsthead
%
%ID & RA & Dec &  $i$ & $z_{\rm phot}$ & $R_{\rm A}$ & Rank & Type & previous ID  \\
%    & (hms) & (dms) &  (mag) &   & (arcsec) &  &  & \\ [1.5ex] \hline \\ 
%\endhead
%
%\hline  
%\multicolumn{11}{p{15cm}}{
%{\bfseries
%{\bf m:} This galaxy falls within the masked region as per the catalog from
%which the magnitudes and the redshift are extracted.  {\bf z:} The magnitudes
%and/or redshift are not from the catalog instead are measured by the author.
%}  }\\
%
%\endlastfoot
%   SW1  & 02:01:21.89 & $-$09:15:15.09 & 19.90 &  0.46 &  2.2 &   2.0 & A &  SA18 \\ 
%   SW2  & 02:02:10.50 & $-$11:09:11.68 & 17.80 &  0.48 &  5.0 &   3.7 & A &  SA87 \\ 
%\end{longtable*}
%

\begin{figure*}
\begin{center}
\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_2p0_3p0.pdf}
\caption{ \label{fig:lch1}
Sample of promising lens candidates ($R_{avg}>=2.0$)
}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_2p0_3p0_1.pdf}
\caption{ \label{fig:lch2}
contd. - Sample of promising lens candidates ($R_{avg}>=2.0$)
}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_1p3_1p7.pdf}
\caption{ \label{fig:lcl}
Sample of low probability lens candidates ($1.0<R_{avg}<2.0$)
}
\end{center}
\end{figure*}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\subsection{Recovery of known \cfhtls lenses from \sw}
\label{sec:results:reco}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\subsection{\cfhtls completeness and purity}
\label{sec:results:sample}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\subsection{Stage 1 Classification}
\label{sec:results:stage1}

\subsection{Stage 2 Classification}
\label{sec:results:stage2}

\subsection{Comparison with ``Expert'' Classification}
\label{sec:results:experts}

@@

Further work.

@@

{\bf TBD: 
add section on offline analysis - extra lenses found etc;  
expand FP section;  
mention EGS moustakas and other lens samples; 
comment on any lensed quasars, on any exotic lenses;
check if some candidates were detected because they were hidden
underneath the sims ie. from the D11;

}

We looked at the locations of simulated and real lenses from our data
those were missed by \sw compared to the locations of the lenses that
got detected. The real lens sample consists of a total of 383 candidates
which have $P_l>2.e-5$ and received a rank of $R_{avg}>0$ from the
expert. We do not find any obvious dependency in the rate of detections
as a function of the position of a given lens for both simulated and
real lens sample. Thus, the completeness of the lens sample is not
affected by whether a lens is located close to the border or well within
the center (see  Figure~\ref{fig:comppos}).

>>>>

\title[\sw II]
{\SW: II. New lens candidates from the CFHTLS discovered
through citizen science}

@@

The CFHT Legacy Survey has been searched for strong lenses with
semi-automated algorithms both at galaxy and groups scales. With the aim
of improving these lens finding robots, we carry out a blind lens search
in the complete \cfhtls \textsc{wide} survey with \sw. We describe the training
sample used for both training the citizen scientists that participated
in \sw and calibrating their performance. We generate realistic looking
simulated samples of lenses both at galaxy and group-scales as part of
this training sample. We present 61 new strong gravitational lens
candidates discovered from the \sw-\cfhtls search out of which 40
candidates are promising. Furthermore, we compile a sample of false
positives which can be used for robot testing, first of its kind for the
lensing community. The simulated sample is also used to make a
comparison between human performance against the robots. We find that
the XX per cent of the known lens sample is recovered and the new lens
sample has XX completeness with respect to the simulated sample. We make
available the following data products: simulated sample, simulation code
and the false positives sample at XXX.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=1.2]{sw-cfhtls-figs/distrib_remu.pdf}
\caption{ \label{fig:remudist}
Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
curves show the theoretical prediction assuming an SIS model at galaxy-scales
and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
}
\end{center}
\end{figure}

@@

\subsection{\sw Lens Sample}
Here, we describe

\subsubsection{Selection of \sw lens candidates}
\label{sec:results:stage1}
The images inspected at stage II are assigned P values through the SWAP
built in the \sw system. Ideally, we would like to have all real lens
candidates to be assigned high P values. It is not known a priori what
value of P would give an optimal trade off between high completeness
and high purity.

Also, since this is the first lens search with \sw, we
would like to understand how the P correspond to the grades, typically,
assigned by lens experts.

\begin{figure}
\begin{center}
\includegraphics[scale=1.2]{sw-cfhtls-figs/poffl_expr_ncl.pdf}
\caption{ \label{fig:exp_pn} Comparison of the P(lens) with the expert
grades and number of classification for each subject.  }
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.6]{sw-cfhtls-figs/cand_fp_P.pdf}
\caption{ \label{fig:stackP} Total number of detections of the known
candidates, new candidates and the FPs shown relatively for binned
values of P.
}
\end{center}
\end{figure}

\subsubsection{New lens candidates from \sw}
\label{sec:results:disc}

{\bf \textcolor{red} {
CHECK FOR STAGE 1 -- COMPLETENESS OF SIMS AND KNOWN LENSES
and P value comparison, what about the duplicate lenses near the borders
- stats on those?}}

@@

\begin{table}
\begin{center}
\caption{ \label{tab:stats} 
Statistics of detections in \sw }
\begin{tabular}{l l l l l l}
\hline
   &  \multicolumn{2}{c} {Stage I}  & \multicolumn{3}{c}{Stage II} \\ 
      & KnCa  &  KnCo  & KnCa & KnCo & NeCa \\
\hline
\hline
Number  & 128 & 34 & 107  & 34  & 61 \\
\%  & 29 & 58 & 25 & 58  & XX \\
P(lens) & 0.95 & 0.95 & 0.3 & 0.3 & 0.3 \\

%% ####stage1
%% cand 128/436
%% conf  34/59

%% ####stage 2
%% sarcs conf 18/26
%% sarcs cand  55/106
%% RF conf 16/33
%% RF cand  52/330

\hline
\end{tabular}
\end{center}
{KnCa}-- Known lens candidates \\
{KnCo}-- Known confirmed lenses \\
{NeCa}-- New lens candidates  \\
\end{table}

\onecolumn

\begin{center}
\begin{longtable}{lrrrrrrrrrr}
\caption{ \label{tab:swcands} 
Sample of the \sw new lens candidates. }\\
\hline
SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm A}$ & G & ZooID & P & Comments  \\
  &  & (deg) & (deg) &  & (mag) &  (") &  &  & & \\ 
\hline
\endfirsthead
\hline
SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm A}$ & G & ZooID & P & Comments  \\
  &  & (deg) & (deg) &  & (mag) &  (") &  &  & & \\ 
\hline
\endhead
\hline
\multicolumn{11}{p{18cm}}{
The column Comments has two type of notes. The first is about the lens
image configuration where the symbols mean the following A: Arc, D: Double, Q:
Quad, R: Ring. The second is a comment on the type of lens assessed
visually. Note that this classification is not based on colors or spectral
analysis. The symbols are E: Elliptical, S: (face on) Spiral, G: Group-scale, D:
Edge on disk, R: Red starforming galaxy.  This galaxy falls within the masked region as per the catalog from
which the magnitudes and the redshift are extracted.  
}\\  
\endlastfoot
 SW1 & CFHTLS J022409-105807 &   36.0398 &  -10.9688 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0  &  A,G   \\ 
 SW2 & CFHTLS J140522+574333 &  211.3426 &   57.7259 &  0.7 & 19.7 &  1.0 &  2.7 & ASW000619d &  0.7  &  A,R   \\ 
 SW3 & CFHTLS J142603+511420 &  216.5149 &   51.2390 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7  &  A,G   \\ 
 SW4 & CFHTLS J142934+562541 &  217.3926 &   56.4281 &  0.5 & 19.0 &  5.9 &  2.7 & ASW0009cjs &  0.8  &  A,G   \\ 
 SW5 & CFHTLS J143454+522850 &  218.7270 &   52.4808 &  0.6 & 19.4 &  4.4 &  2.7 & ASW0007k4r &  0.4  &  Q,G/R   \\ 
 SW6 & CFHTLS J143627+563832 &  219.1164 &   56.6425 &  0.5 & 19.4 &  1.5 &  2.7 & ASW0008swn &  0.9  &  A,D   \\ 
 SW7 & CFHTLS J220256+023432 &  330.7369 &    2.5758 &  0.0 &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8  &  A,G/C   \\ 
 SW8 & CFHTLS J020832-043315 &   32.1340 &   -4.5543 &  1.0 & 21.0 &  1.6 &  2.3 & ASW0002asp &  1.0  &  A,R   \\ 
 SW9 & CFHTLS J020848-042427 &   32.2011 &   -4.4075 &  0.8 & 20.5 &  1.1 &  2.3 & ASW0002bmc &  0.9  &  D,D   \\ 
SW10 & CFHTLS J020849-050429 &   32.2078 &   -5.0749 &  0.8 & 20.6 &  0.9 &  2.3 & ASW0002qtn &  1.0  &  A,R   \\ 
SW11 & CFHTLS J022406-062846 &   36.0256 &   -6.4796 &  0.4 & 19.6 &  0.9 &  2.3 & ASW0003wsu &  0.7  &  A,E   \\ 
SW12 & CFHTLS J022805-051733 &   37.0236 &   -5.2927 &  0.4 & 18.8 &  1.4 &  2.3 & ASW0009ans &  1.0  &  Q,E   \\ 
SW13 & CFHTLS J023123-082535 &   37.8468 &   -8.4266 &  0.0 &  0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3  &  A,R   \\ 
SW14 & CFHTLS J084841-045237 &  132.1708 &   -4.8772 &  0.3 & 19.0 &  1.0 &  2.3 & ASW0004nan &  1.0  &  A,E   \\ 
SW15 & CFHTLS J140030+574437 &  210.1260 &   57.7437 &  0.4 & 18.2 &  2.0 &  2.3 & ASW0009bp2 &  0.6  &  A,E   \\ 
SW16 & CFHTLS J140622+520942 &  211.5958 &   52.1617 &  0.7 & 20.3 &  1.2 &  2.3 & ASW0005rnb &  0.7  &  A,R   \\ 
SW17 & CFHTLS J143658+533807 &  219.2425 &   53.6355 &  0.7 & 19.6 &  0.9 &  2.3 & ASW0007hu2 &  0.6  &  D,D   \\ 
SW18 & CFHTLS J020642-095157 &   31.6750 &   -9.8658 &  0.2 & 20.8 &  0.9 &  2.0 & ASW0001ld7 &  0.8  &  A,R   \\ 
SW19 & CFHTLS J021221-105251 &   33.0881 &  -10.8811 &  0.3 & 17.9 &  1.8 &  2.0 & ASW0002dx7 &  0.8  &  D,E/S   \\ 
SW20 & CFHTLS J022533-053204 &   36.3888 &   -5.5346 &  0.5 & 19.4 &  3.6 &  2.0 & ASW0004m3x &  0.4  &  A,R/G   \\ 
SW21 & CFHTLS J022716-105602 &   36.8186 &  -10.9341 &  0.4 & 17.2 &  1.8 &  2.0 & ASW0009ab8 &  0.7  &  A,E/G   \\ 
SW22 & CFHTLS J023008-054038 &   37.5359 &   -5.6774 &  0.6 & 19.7 &  1.9 &  2.0 & ASW0003r61 &  0.5  &  A,E   \\ 
SW23 & CFHTLS J023051-082423 &   37.7141 &   -8.4064 &  0.0 &  0.0 &  0.8 &  2.0 & ASW000412m &  0.4  &  A,E   \\ 
SW24 & CFHTLS J023315-042243 &   38.3133 &   -4.3789 &  0.7 & 19.7 &  1.0 &  2.0 & ASW00050sk &  0.8  &  A,R   \\ 
SW25 & CFHTLS J090308-043252 &  135.7844 &   -4.5479 &  0.0 &  0.0 &  1.2 &  2.0 & ASW00007mq &  0.6  &  A,E   \\ 
SW26 & CFHTLS J135755+571722 &  209.4827 &   57.2897 &  0.8 & 20.2 &  1.3 &  2.0 & ASW0005ma2 &  0.8  &  D,D   \\ 
SW27 & CFHTLS J141432+534004 &  213.6372 &   53.6679 &  0.7 & 21.4 &  0.9 &  2.0 & ASW0006jh5 &  0.8  &  A,R   \\ 
SW28 & CFHTLS J143055+572431 &  217.7333 &   57.4088 &  0.7 & 19.3 &  1.0 &  2.0 & ASW0007wfj &  0.9  &  A,R   \\ 
SW29 & CFHTLS J143838+572647 &  219.6589 &   57.4464 &  0.8 & 20.2 &  1.1 &  2.0 & ASW0008qsm &  0.9  &  A,R   \\ 
SW30 & CFHTLS J021057-084450 &   32.7414 &   -8.7474 &  0.0 &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4  &  A,G   \\ 
SW31 & CFHTLS J021514-092440 &   33.8109 &   -9.4111 &  0.7 & 19.9 &  2.6 &  1.7 & ASW00021r0 &  0.4  &  A,R/G   \\ 
SW32 & CFHTLS J022359-083651 &   35.9995 &   -8.6143 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4  &  A,E   \\ 
SW33 & CFHTLS J022745-062518 &   36.9387 &   -6.4218 &  0.6 & 20.5 &  1.2 &  1.7 & ASW0003s0m &  0.5  &  A,R   \\ 
SW34 & CFHTLS J023453-093032 &   38.7232 &   -9.5089 &  0.5 & 19.8 &  0.7 &  1.7 & ASW00051ld &  0.3  &  A,D   \\ 
SW35 & CFHTLS J084833-044051 &  132.1385 &   -4.6809 &  0.8 & 20.2 &  0.9 &  1.7 & ASW0004wgd &  0.7  &  A,R   \\ 
SW36 & CFHTLS J090248-010232 &  135.7020 &   -1.0424 &  0.4 & 19.1 &  1.4 &  1.7 & ASW000096t &  0.6  &  D,E   \\ 
SW37 & CFHTLS J143100+564603 &  217.7511 &   56.7675 &  0.0 &  0.0 &  1.8 &  1.7 & ASW00086xq &  0.8  &  A,E   \\ 
SW38 & CFHTLS J143353+542310 &  218.4736 &   54.3862 &  0.8 & 19.8 &  1.6 &  1.7 & ASW0009cox &  0.6  &  A,R/G   \\ 
SW39 & CFHTLS J220215+012124 &  330.5635 &    1.3567 &  0.3 & 17.4 &  4.6 &  1.7 & ASW0005qiz &  0.5  &  rA,G   \\ 
SW40 & CFHTLS J221306+014708 &  333.2758 &    1.7856 &  0.0 & 17.1 &  1.4 &  1.7 & ASW0008wmr &  0.9  &  A,S   \\ 
SW41 & CFHTLS J221513+010240 &  333.8056 &    1.0446 &  0.0 &  0.0 &  0.8 &  1.7 & ASW0008dxh &  0.3  &  A,R/G   \\ 
SW42 & CFHTLS J221519+005758 &  333.8321 &    0.9661 &  0.4 & 20.2 &  1.0 &  1.7 & ASW0008xbu &  0.8  &  A,D   \\ 
SW43 & CFHTLS J221716+015826 &  334.3189 &    1.9739 &  0.1 & 21.6 &  1.0 &  1.7 & ASW00096rm &  1.0  &  A/R,R   \\ 
SW44 & CFHTLS J020810-040220 &   32.0450 &   -4.0389 &  1.0 & 20.8 &  1.8 &  1.3 & ASW0001c3j &  0.7  &  A,R   \\ 
SW45 & CFHTLS J021021-093415 &   32.5898 &   -9.5711 &  0.4 & 18.4 &  2.7 &  1.3 & ASW0002k40 &  0.4  &  D,S   \\ 
SW46 & CFHTLS J021225-085211 &   33.1051 &   -8.8697 &  0.8 & 19.5 &  2.1 &  1.3 & ASW00024id &  1.0  &  R,R   \\ 
SW47 & CFHTLS J021317-084819 &   33.3234 &   -8.8055 &  0.5 & 19.8 &  1.3 &  1.3 & ASW00024q6 &  0.4  &  A,R/E   \\ 
SW48 & CFHTLS J022843-063316 &   37.1794 &   -6.5547 &  0.5 & 19.1 &  1.8 &  1.3 & ASW0003r6c &  0.3  &  D/A,E   \\ 
SW49 & CFHTLS J090219-053923 &  135.5794 &   -5.6566 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0  &  A,R/E   \\ 
SW50 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  0.0 & 19.8 &  1.2 &  1.3 & ASW00007ls &  0.5  &  A,R/E   \\ 
SW51 & CFHTLS J090333-005829 &  135.8886 &   -0.9749 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0  &  A/D,E/G   \\ 
SW52 & CFHTLS J135724+561614 &  209.3536 &   56.2707 &  0.0 &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9  &  D,E   \\ 
SW53 & CFHTLS J140027+541028 &  210.1164 &   54.1746 &  0.0 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6  &  Q,R/E   \\ 
SW54 & CFHTLS J140425+520506 &  211.1062 &   52.0850 &  0.4 & 18.9 &  1.4 &  1.3 & ASW0005o0w &  0.6  &  D,E   \\ 
SW55 & CFHTLS J141518+513915 &  213.8290 &   51.6542 &  0.4 & 18.3 &  3.0 &  1.3 & ASW00070vl &  0.8  &  D,E   \\ 
SW56 & CFHTLS J142620+561356 &  216.5870 &   56.2323 &  0.5 & 19.5 &  1.3 &  1.3 & ASW0007sez &  0.8  &  A/R,S   \\ 
SW57 & CFHTLS J142652+560002 &  216.7201 &   56.0006 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0  &  R,R   \\ 
SW58 & CFHTLS J142843+543713 &  217.1815 &   54.6204 &  0.4 & 19.7 &  1.3 &  1.3 & ASW0007pga &  0.6  &  D,D   \\ 
SW59 & CFHTLS J143631+571131 &  219.1315 &   57.1922 &  0.7 & 20.9 &  1.3 &  1.3 & ASW0008pag &  0.6  &  D/A,R   \\ 
SW60 & CFHTLS J143651+530705 &  219.2150 &   53.1183 &  0.6 & 19.2 &  3.1 &  1.3 & ASW0007h27 &  1.0  &  A,E/G   \\ 
SW61 & CFHTLS J143950+544606 &  219.9609 &   54.7686 &  0.0 &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4  &  A,G/R   \\ 
\end{longtable}
\end{center}

\twocolumn

\begin{figure*}
\begin{center}
\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin.pdf}
\caption{ \label{fig:lc}
Sample of lens candidates with G$>=$1.3.
}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin_1.pdf}
\caption{ \label{fig:lc1}
Sample of lens candidates G$>=1.3$.
}
\end{center}
\end{figure*}

\subsection{Recovery of known \cfhtls lenses with \sw}
\label{sec:results:known}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/comp_reinst_mag.pdf}
\caption{ \label{fig:compre} Fraction of lens candidates detected by \sw
as a function of the Einstein radius and arc $g$ band magnitudes for
three lens samples, namely, simulated lenses, known confirmed lenses and
the lens candidates sample. XXXX sims are stage1 and real sample values
are for stage 2. }
\end{center}
\end{figure*}

@@

\subsection{Image separation distribution}
\label{sec:results:isd}

\begin{figure}
\begin{center}
\includegraphics[scale=1.2]{sw-cfhtls-figs/isd_cfhtls_sw.pdf}
\caption{ \label{fig:isd} Image separation distribution. Comparing
theoretical predictions with the \cfhtls known lens samples (REF) and
the same \cfhtls sample after combining with the incremental lens sample
from \sw }
\end{center}
\end{figure}

@@

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.65]{sw-cfhtls-figs/zl_mg_re.pdf}
\caption{ \label{fig:zlre}
Comparison of Lens redshift and magnitude as a function of Arc radius for all three lens samples,
namely, from \sw, SARCS and those from the RingFinder. Also,
corresponding histograms are shown.}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.6]{sw-cfhtls-figs/stacked_lenscand_rein.pdf}
\includegraphics[scale=0.6]{sw-cfhtls-figs/stacked_lenscand_mag.pdf}
\caption{ \label{fig:stackre}
Detections by three methods the Ringfinder, \sw and the Arcfinder as a
function of the Einstein radius and $g$ band magnitude of the lensed
images. XXXX check how different are the estimates from the different measurement techniques for a given lens candidates. }
\end{center}
\end{figure}

{\bf TBD: 
add section on offline analysis - extra lenses found etc;  
expand FP section;  
mention EGS moustakas and other lens samples; 
comment on any lensed quasars, on any exotic lenses;
check if some candidates were detected because they were hidden
underneath the sims ie. from the D11;
}

\subsection{Blind Lens Search}
We looked at the locations of simulated and real lenses from our data
those were missed by \sw compared to the locations of the lenses that
got detected. The real lens sample consists of a total of XXXX candidates
which have $P_l>2.e-5$XXXXX (check this) and received a rank of G$>0$ from the
expert. We do not find any obvious dependency in the rate of detections
as a function of the position of a given lens for both simulated and
real lens sample. Thus, the completeness of the lens sample is not
affected by whether a lens is located close to the border or well within
the center (see  Figure~\ref{fig:comppos}).
